\begin{thebibliography}{00}
    \bibitem{b1} Kgremban, “Azure Iot Hub Communication Protocols and Ports,” Azure IoT Hub communication protocols and ports | Microsoft Learn, 14-Jun-2022. [Online]. Available: \url{https://learn.microsoft.com/en-us/azure/iot-hub/iot-hub-devguide-protocols}. [Accessed: 02-Nov-2022]. 

    \bibitem{b2} I. Craggs, “Mqtt vs AMQP for IOT,” HiveMQ, 29-Jun-2022. [Online]. Available: \url{https://www.hivemq.com/blog/mqtt-vs-amqp-for-iot/#:~:text=MQTT%20vs%20AMQP%3A%20Understanding%20the%20Differences&amp;text=AMQP%20was%20designed%20to%20provide,is%20more%20complex%20than%20MQTT}. [Accessed: 02-Nov-2022]. 
    
    \bibitem{b3} I. Craggs, “MQTT vs. HTTP: Which protocol is the best for IOT or Iiot?,” MQTT vs HTTP for IoT, 16-May-2022. [Online]. Available: \url{https://www.hivemq.com/blog/mqtt-vs-http-protocols-in-iot-iiot/}. [Accessed: 02-Nov-2022]. 
    
    \bibitem{b4} KaiserLee, “Why bluetooth iot?” MOKOBlue, 13-Oct-2021. [Online]. Available: \url{https://www.mokoblue.com/why-bluetooth-iot/#:~:text=In%20today%27s%20technology%20world%2C%20Bluetooth,magnificent%20range%2C%20and%20amplified%20connectivity}. [Accessed: 06-Nov-2022]. 
    
    \bibitem{b5} R. Katila, T. N. Gia, and T. Westerlund, “Analysis of mobility support approaches for edge-based IOT systems using high data rate Bluetooth Low Energy 5,” Computer Networks, 26-Mar-2022. [Online]. Available: \url{https://www.sciencedirect.com/science/article/pii/S1389128622001141}. [Accessed: 06-Nov-2022].
    
    \bibitem{b6} J. Hopkins, “Understanding the Differences Between UART and USB” Total Phase, 26-Jan-2022. [Online]. Available: \url{https://www.totalphase.com/blog/2022/01/understanding-differences-between-uart-and-usb/}. [Accessed: 06-Nov-2022].

    \bibitem{b7} Apogeeweb, “Which Battery Can Replace CR2032?” Apogee Web, 14-May-2021. [Online]. Available: \url{https://www.apogeeweb.net/electron/what-battery-is-equivalent-to-CR2032.html}. [Accessed: 06-Nov-2022].
    % Just as example: \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\end{thebibliography}