\section{Cost Analysis}
Regarding the cost we chose to divide it into two sections, the unit cost of the device and the cost of the cloud.

\subsection{Unitary costs}
The main cost of the device is from the components themselves. Therefore the following
table will gather each of the selected components and their cost (converted from USD
if necessary with the rate 1\$ = 0.96€).\\

\begin{table}[htbp]
    \centering
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Component} & \textbf{Price €} \\
        \hline
         Board ESP32-PICO-D4 & 4.95 \\
         Temperature sensor HTU31 & 5.35 \\
         Light sensor TSL2591 & 5.35 \\
         Ph sensor SEN016 & 26.00 \\
         CR2450 battery & 7.31 \\
         \hline
         \textbf{Total} & \textbf{48.96}\\
         \hline
    \end{tabular}
    \caption{Price of each selected component}
    \label{tab:my_label}
\end{table}

The total cost of the device's components is 48.96€. Moreover since the battery CR2450
is rechargeable there won't be a need to replace the battery as it can simply get
charged once the battery runs low.

\subsection{Cloud subscription}
The cloud services we use are AWS IoT, AWS Lambda, AWS DynamoDB, AWS Cognito and AWS
SNS. \\
The pricing estimate for the cloud services is based on three potential situations:
\begin{itemize}
    \item A closed beta period, with not many users, a few thousand devices in
          total (5000 devices)
    \item After the launch and widespread deployment, assuming a big number of users
          (100.000 devices)
\end{itemize}

\subsubsection{Closed Beta Period}
During this hypothetical closed beta period, we would have a few thousand devices in total.
As such, the following services would be necessary:
\begin{itemize}
    \item A DynamoDB containing readings and calculations, with a capacity, at peak, of
          20 GBs, with less than a million reads happening per month and at most
          20000 writes per day. This, using the on-demand services of DynamoDB, would cost
          \$6.66 per month, most of the cost being storage related (this is thus
          a "worst-case" estimate).
    \item AWS Lambdas, which would be used to execute data analysis on the readings
          and to send notifications to the users. The number of executions would
          be at most 10000 per day, and the memory used would be at most 512MB
          as there's yet not much data to analyze. Assuming our lambdas would not
          run for more than 1 second each (which is already a gross overestimation
          of actual execution time), we would still fit into the "Always Free" tier
          of AWS Lambda.
    \item AWS Cognito with 5000 users. This still fits the free tier.
    \item AWS IoT Core, with 5000 devices, sending 50 messages a month each of 
          up to 4KBs, each triggering up to 2 rules. This would cost \$0.42 per
          month.
    \item AWS API Gateway, with ~20.000 API calls per day. This would cost \$2.13
          per month, assuming we use the REST API option.
    \item AWS SNS, with at most 10.000 notifications per day. This still fits the
          free tier.
\end{itemize}

This all comes up to a total of \$9.21 per month, which is \$0.001842 per device
per month, or \$0.0221 per device per year.

\subsubsection*{After the launch}
After launch and widespread deployment, we should be able to support up to 100.000
users. This would mean that the following services would be necessary:
\begin{itemize}
    \item A DynamoDB containing readings and calculations, with a capacity, at peak, of
          512 GBs, with up to 500.000 reads happening per day and up to
          200.000 writes per day. This, using the on-demand services of DynamoDB,
          sums up to \$155.65 per month.
    \item AWS Lambdas. These should be now split
          into two tiers, one for the data analysis and one for the notifications.
          \begin{itemize}
            \item Data analysis: 200.000 executions per day, with up to 2GB of memory
                  used per execution. This would cost \$204 per month.
            \item Notifications: Up to 500.000 executions per day, with at most
                  128MB of memory used per execution. This would cost \$2.84 per
                  month.
          \end{itemize}
    \item AWS Cognito with 100.000 users. This costs \$275 per month.
    \item AWS IoT Core, with 100.000 devices, sending 50 messages a month each of 
          up to 4KBs, each triggering up to 2 rules. This would cost \$8.45 per
          month.
    \item AWS API Gateway, with ~500.000 API calls per day. This would cost \$53.23
          per month, assuming we use the REST API option.
\end{itemize}

This all comes up to a total of \$699.17 per month, which is \$0.0069917 per device
per month, or \$0.0839004 per device per year.