\section{Market study}

\subsection{Competitors and similar products}
There are a few available options on the market that somewhat match the product
we have in mind, such as:

\begin{itemize}
    \item Huahuacaocao Flower Care Smart Monitor \textasciitilde{} 31.64€
    \item WANFEI Intelligent 4 in 1 Plant Monitor \textasciitilde{} 30.63€
    \item OLLIVAN Plant Monitor Smart Plan \textasciitilde{} 27.80€
\end{itemize}

Unfortunately these options present some non negligible disadvantages. They all
have the exact same design and characteristics and are sold on websites such as
Aliexpress and Amazon. 

The Huahuacaocao is a Xiaomi product and perhaps the most reliable of them all.
However customer product review are mainly negative, and focus on both sensor inaccuracy
and software usability, but also mentions connectivity issues between the device
and the app. The table below identifies all characteristics found in this product. 

\begin{table}[htbp]
\caption{Market product functionalities}
\begin{center}
\renewcommand{\arraystretch}{2}
\begin{tabular}{|c|c|c|}
\hline
\textbf{\textit{Description}}& \textbf{\textit{Sensors}}& \textbf{\textit{Performance}} \\
\hline
\begin{minipage} [t] {0.15\textwidth} 
\underline{Size}: 120.5 x 24.5 x 12.5 mm\\
\underline{Weight}: 18.14g\\
\underline{Battery}: CR2032 button cell battery\\
\underline{Wireless connectivity}: Bluetooth 4.1\\
\end{minipage} & 
\begin{minipage} [t] {0.15\textwidth} 
\underline{Moisture}: long black strip sensor (EC5 standard)\\
\underline{Light}: light intensity up to 100,000LUX with accuracy of 100LUX\\
\underline{Temperature}: accuracy of the temperature can go up to 0.5 ℃\\
\underline{Nutrients}: 4 EC sensors (stainless steel)\\
\end{minipage}  &
\begin{minipage} [t] {0.15\textwidth} 
\underline{Database}: 3000 different types of plants\\
\underline{Operating voltage}: 3V\\
\underline{Battery duration}: 365 days\\
\underline{CMIIT ID}: 2016DP0940\\

\end{minipage} \\
\hline
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\subsection{Target customers}
Due to all this negative feedback of the products on the market there is no real
solution out there capable of satisfying the customers needs. 

Therefore we are hoping with our product to help people who have been struggling
at maintaining a healthy home plant. Either by getting them organized with a watering
schedule, or by warning them of potential environmental risks the plant may encounter.
But it is also an opportunity for plant enthusiast to monitor their plant and become
a part of the plant profile community to learn and share about the best living conditions
of their home plants. 
